% Cover Letter for Paralympics Australia IT Internship
\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

% Page layout
\geometry{
	a4paper,
	left=2.5cm,
	right=2.5cm,
	top=2.5cm,
	bottom=2.5cm
}

% Hyperlink setup
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=blue,
	pdfborder={0 0 0}
}

% Remove indentation from paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}
	
	% Sender information
	\begin{flushright}
		\textbf{Cameron Badman}\\
		Email: \href{mailto:cbadwork@gmail.com}{cbadwork@gmail.com}\\
		Phone: +61 476056341\\
		\href{https://github.com/CameronBadman}{GitHub} | \href{https://www.linkedin.com/in/cameron-badman-5314ba1b8/}{LinkedIn}\\
	\end{flushright}
	
	\vspace{0.5cm}
	\noindent April 14, 2025
	
	\vspace{0.5cm}
	\noindent Melanie Davis\\
	Paralympics Australia\\
	53 Albert Street\\
	Brisbane, QLD, 4000\\
	Australia
	
	\vspace{0.5cm}
	\noindent Dear Ms. Davis,
	
	\vspace{0.3cm}
	I am writing to express my enthusiasm for the Information Technology Intern position at Paralympics Australia. As a Computer Science and Commerce student at the University of Queensland, I am excited by the opportunity to contribute to an organization that makes such a meaningful impact on Australian athletes and the broader community.
	
	Through my studies and project work, I have developed a foundation in programming and data concepts that I'm eager to apply in a professional setting. While I don't have specific Salesforce experience, I am enthusiastic about learning this platform and how it can be optimized to support your organization's needs. I am particularly excited about gaining hands-on experience with CRM systems, data migration, and creating reports and dashboards that provide meaningful insights.
	
	My experience as a Python tutor has helped me develop strong communication skills and the ability to explain technical concepts clearly. I believe these skills would be valuable in documenting processes and providing user support across your organization. I'm comfortable working with Excel and have a genuine interest in data structures that I'm eager to develop further.
	
	Thank you for considering my application. I look forward to the possibility of discussing how my enthusiasm for learning, communication skills, and passion for purposeful work could contribute to your team.
	
	\vspace{0.5cm}
	\noindent Sincerely,
	
	\vspace{1cm}
	\noindent Cameron Badman
	
\end{document}